Test of Adaptable User Interfaces

### 2015-07-08 paper.tex
Adding comparator feature screenshot for the case study
First version of the case study with the images

@@

\marginpar{
\begin{figure}
  \begin{center}
  \includegraphics[width=\marginparwidth]{images/web0_goal-filter.eps}
  \caption{Une figure dans la marge.}
  \label{fig:marginparsample}
  \end{center}  
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=\marginparwidth]{images/mobile_goal-filter.eps}
  \caption{Une figure dans la marge.}
  \label{fig:marginparsample}
  \end{center}  
\end{figure}
}

@@

\begin{enumerate}

\item \textbf{Goal}: the user can check information about the general energy consumption per month. Having access to the goal and consumption in kWh for the chosen month.

\item \textbf{Filter}: the user has access to a list of all his or her objects in the house, having the possibility to filter this list per room. An object means any component that can be controlled and whose energy consumption can be registered, such as lights and electronic devices.

\item \textbf{Comparator}: the user can choose two objects and compare, side by side, their energy consumption charts. This feature is present in only two of the web versions.

\end{enumerate}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{images/web0_goal-filter.eps}
  \caption{Ajoutez une légende en dessous de chaque image.}
  \label{fig:sample}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{images/mobile_goal-filter.eps}
  \caption{Ajoutez une légende en dessous de chaque image.}
  \label{fig:sample}
\end{figure}

>>>>

\marginpar{
\begin{figure}
  \begin{center}
  \includegraphics[width=\marginparwidth]{images/web0_goal-filter.eps}
  \caption{Web version. Number 1 represents the \textbf{goal} feature and number 2 represents the \textbf{filter} feature.}
  \label{fig:web0print}
  \end{center}  
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=\marginparwidth]{images/mobile_goal-filter.eps}
  \caption{Mobile version. Number 1 represents the \textbf{goal} feature and number 2 represents the \textbf{filter} feature.}
  \label{fig:mobileprint}
  \end{center}  
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=\marginparwidth]{images/web1_comparator.eps}
  \caption{Other web version. Number 3 represents the \textbf{comparator} feature.}
  \label{fig:web1print}
  \end{center}  
\end{figure}
}

@@

@@

\begin{enumerate}
\item \textbf{Goal}: the user can check information about the general energy consumption per month. Having access to the goal and consumption in kWh for the chosen month. See \autoref{fig:web0print} and \autoref{fig:mobileprint}.

\item \textbf{Filter}: the user has access to a list of all his or her objects in the house, having the possibility to filter this list per room. An object means any component that can be controlled and whose energy consumption can be registered, such as lights and electronic devices. See \autoref{fig:web0print} and \autoref{fig:mobileprint}.

\item \textbf{Comparator}: the user can choose two objects and compare, side by side, their energy consumption charts. This feature is present in only two of the web versions. See \autoref{fig:web1print}
\end{enumerate}

The purpose is to test each feature using execution automation tools for UI testing. For instance Selenium~\cite{selenium} for the web versions and Selendroid~\cite{selendroid} for the mobile version. The approach to test the \textbf{goal} feature is to make these tools to change the current month, interacting with the combobox filter component, and then to verify if the goal and consumed labels have the right value. In the case of the \textbf{filter} feature, the tools have to interact with the filter, changing the current room and verifying if the only correct objects are displayed in the screen. Finally, the \textbf{compator} feature can be tested by using the tools to change the room filter, to chose the objects using the checkbox and to verify if the charts are displayed.
